---
title: "Airbnb Review Scores Rating Exploration and Prediction: Empirical Evidence from Hong Kong"
date: "10/12/2020"
authour: Minhui Ma
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, warning = FALSE)
```

## Introduction
This empirical project aims to analysis the determinants of Airbnb review scores rating and do review scores rating prediction.

This project is available on Github [`minhui-ma/Airbnb-Empirical-Projrect`](https://github.com/minhui-ma/Airbnb-Empirical-Projrect).

## Import data
A data exploration analysis is firstly carried out to have a initial insight into the three datasets - Listings, Reviews, and Calender.

```{r}
# import packages
library(tidyverse)
library(geojsonio)
library(ggplot2)
library(plotly)
library(BBmisc)
library(corrplot)
library(e1071)
library(skimr)
library(stargazer)
```

```{r}
# import data
listings <- read.csv("listings.csv", header = TRUE, sep = ",")
# reviews <- read.csv("reviews.csv", header = TRUE, sep = ",")
# calendar <- read.csv("calendar.csv", header = TRUE, sep = ",")
# neighbourhoods <- read.csv("neighbourhoods.csv", header = TRUE, sep = ",")

# import map
# spdf <- geojson_read("neighbourhoods.geojson", what = "sp")
```

## Data cleansing

* Replace all empty values with NA 
* Drop all empty columns
* Filter out rows with ```review_scores_rating``` in NA
* Drop columns with same value
* For missing review scores of the 6 dimensions, let them equal to the ```review_scores_rating```
* Convert currency values to numeric values
* Replace date variables, we only need its year
* Convert percentage values to numeric values, and replace missing values with 0
```{r}
listings[listings==''] <- NA
listings[listings=='N/A'] <- NA
listings2 <- listings[!sapply(listings,function(x)all(is.na(x)))]
listings2 <- listings2 %>% filter(review_scores_rating != '')
listings2 <- listings2 %>% select(where(~length(unique(.)) > 1))

review_scores <- c('review_scores_accuracy','review_scores_checkin','review_scores_communication',
                   'review_scores_cleanliness','review_scores_value','review_scores_location')
for (i in review_scores){
  text <- paste("listings2$",i," <- ifelse(is.na(listings2$",i,"),listings2$review_scores_rating*0.1,listings2$",i,")",sep='')
  eval(parse(text= text))
}

listings2$price <- as.numeric(gsub('[$,]', '', listings2$price))
listings2$weekly_price <- as.numeric(gsub('[$,]', '', listings2$weekly_price))
listings2$monthly_price <- as.numeric(gsub('[$,]', '', listings2$monthly_price))
listings2$security_deposit <- as.numeric(gsub('[$,]', '', listings2$security_deposit))
listings2$cleaning_fee <- as.numeric(gsub('[$,]', '', listings2$cleaning_fee))
listings2$extra_people <- as.numeric(gsub('[$,]', '', listings2$extra_people))

var_date <- c('host_since','first_review','last_review')
for (i in var_date){
  text <- paste("listings2$",i," <- floor(as.integer(format(as.Date(listings2$",i,"),'%Y')))",sep='')
  eval(parse(text= text))
}

listings2$host_response_rate <- as.numeric(sub("%","",listings2$host_response_rate))/100
listings2$host_response_rate[is.na(listings2$host_response_rate)] <- 0

listings2$host_acceptance_rate <- as.numeric(sub("%","",listings2$host_acceptance_rate))/100
listings2$host_acceptance_rate[is.na(listings2$host_acceptance_rate)] <- 0
```

* Drop variables
- ```listing_url```, ```picture_url```, ```host_url```, ```host_thumbnail_url```, ```host_picture_url```
- ```host_name```, ```name```
- ```market```, ```state```, ```smart_location```, ```country_code```, ```country```
- ```host_location```, ```host_neighbourhood```, ```street```, ```city```
- ```neighbouthood```
- ```zipcode```, ```square_feet```
- ```availability_30```, ```availability_60```, ```availability_90```, ```availability_365```
- ```last_scraped```, ```calendar_last_scraped```
```{r}
listings2 <- listings2 %>% 
  select(-listing_url, -picture_url, -host_url, -host_thumbnail_url, -host_picture_url,
         -host_name, -name,
         -market, -state, -smart_location, -country_code, -country,
         -host_location, -host_neighbourhood, -street, -city,
         -host_listings_count, -host_total_listings_count, 
         -neighbourhood, 
         -zipcode, -square_feet,
         -availability_30, -availability_60, -availability_90, -availability_365,
         -last_scraped, -calendar_last_scraped,
         -host_id)
```

* Replace t with 1 and f with 0: ```host_has_profile_pic```, ```host_identity_verified```, ```host_is_superhost```, ```is_location_exact```, ```instant_bookable```, ```require_guest_profile_picture```, ```require_guest_phone_verification```
```{r}
listings2 <- listings2 %>% 
  mutate(host_has_profile_pic = ifelse(host_has_profile_pic == "t", 1, 0),
         host_identity_verified = ifelse(host_identity_verified == "t", 1, 0),
         host_is_superhost = ifelse(host_is_superhost == "t", 1, 0),
         is_location_exact = ifelse(is_location_exact == "t", 1, 0),
         instant_bookable = ifelse(instant_bookable == "t", 1, 0),
         require_guest_profile_picture = ifelse(require_guest_profile_picture == "t", 1, 0),
         require_guest_phone_verification = ifelse(require_guest_phone_verification == "t", 1, 0),)

var <- c('host_has_profile_pic','host_identity_verified','host_is_superhost','is_location_exact',
         'instant_bookable','require_guest_profile_picture','require_guest_phone_verification')
for (i in var){
  text <- paste(" listings2$",i,"[is.na(listings2$",i,")] <- 0",sep='')
  eval(parse(text= text))
}
```

* Drop variables: ```summary```,  ```space```, ```description```, ```neighborhood_overview```, ```notes```, ```transit```, ```access```, ```interaction```, ```house_rules```, ```license```, ```host_about```, ```cancellation_policy```
* Drop variable: ```is_location_exact``` - unimportant as it could be inacurate up to 150 meters http://insideairbnb.com/about.html#disclaimers
* Drop variable: ```calendar_updated``` - we are not interested in future data that is a subject to daily updates
```{r}
listings2 <- listings2 %>% 
  select(-summary, -space, -description, -neighborhood_overview, -notes, -transit, -access, -interaction, -house_rules, -license,
         -host_about, -cancellation_policy,
         -is_location_exact,
         -calendar_updated)
```

* Replace missing values with 0: ```bathrooms```,  ```beds```, ```security_deposit```, ```cleaning_fee```
* Replace missing values with the mean value: ```host_since```
* Replace missing values with other values: ```monthly_price```, ```weekly_price```, ```host_response_time```
```{r}
var0 <- c('bathrooms','beds','bedrooms','security_deposit','cleaning_fee')
for (i in var0){
  text <- paste("listings2$",i,"[is.na(listings2$",i,")] <- 0",sep='')
  eval(parse(text= text))
}

listings2$weekly_price[is.na(listings2$weekly_price)] <- 7*listings2$price[is.na(listings2$weekly_price)]
listings2$monthly_price[is.na(listings2$monthly_price)] <- 30*listings2$price[is.na(listings2$monthly_price)]

listings2$host_since[is.na(listings2$host_since)] <- floor(mean(listings2$host_since[!is.na(listings2$host_since)]))

listings2 <- listings2 %>% select(where(~length(unique(.)) > 1))

listings2$host_response_time[is.na(listings2$host_response_time)] <- 'no response'
```

## Exploratory Data Analysis

correlation
```{r}
listings_scores <- listings2 %>% 
  select(review_scores_rating, 
         review_scores_accuracy, 
         review_scores_checkin, 
         review_scores_cleanliness, 
         review_scores_communication,
         review_scores_location, 
         review_scores_value) %>% 
  rename(scores = review_scores_rating, 
         accuracy = review_scores_accuracy, 
         checkin = review_scores_checkin, 
         cleanliness = review_scores_cleanliness, 
         communication = review_scores_communication,
         location = review_scores_location, 
         value = review_scores_value)
corrplot(cor(listings_scores), type = "lower", method = "number")
```

```review_scores_rating``` is an overall score on the AirBnb listing from 0–100. ```reviews_per_month``` is the number of reviews received by a listing per month.
```{r}
ggplot(listings2, aes(x = review_scores_rating)) + 
  geom_histogram(fill="black", colour="black", alpha = 0.25, binwidth=1)
```
```{r}
ggplot(listings2, aes(x = reviews_per_month)) + 
  geom_histogram(fill="black", colour="black", alpha = 0.25, binwidth=1)
```
```{r}
ggplot(listings2, aes(x = number_of_reviews)) + 
  geom_histogram(fill="black", colour="black", alpha = 0.25, binwidth=10)
```

Replace ```review_scores_rating``` with ```cx_scores``` and drop ```review_scores_rating```, ```review_scores_```
```{r}
listings3 <- listings2 %>% 
  mutate(cx_scores = normalize(review_scores_rating, method = "range", range = c(0,1))*reviews_per_month) %>% 
  select(-review_scores_rating, 
         -review_scores_accuracy, 
         -review_scores_checkin, 
         -review_scores_cleanliness, 
         -review_scores_communication,
         -review_scores_location, 
         -review_scores_value,
         -reviews_per_month,
         -number_of_reviews,
         -number_of_reviews_ltm)
```
```{r}
ggplot(listings3, aes(x = cx_scores)) + 
  geom_histogram(fill="black", colour="black", alpha = 0.25, binwidth=1)
```

* property_type
```{r}
ggplot(data = listings3, aes(x = as.character(property_type), y = cx_scores, color = as.character(property_type))) +
  geom_boxplot(outlier.shape = NA) +
  theme(axis.text.x = element_text(angle = 90, hjust = 1),legend.position = "none")+
  coord_cartesian(ylim = c(0, 5)) +
  xlab("property_type")
```

* room_type
```{r}
ggplot(data = listings3, aes(x = as.character(room_type), y = cx_scores, color = as.character(room_type))) +
  geom_boxplot(outlier.shape = NA) +
  theme(axis.text.x = element_text(angle = 90, hjust = 1),legend.title = element_blank())+
  coord_cartesian(ylim = c(0, 3)) +
  xlab("room_type")
```

* bed_type
```{r}
ggplot(data = listings3, aes(x = as.character(bed_type), y = cx_scores, color = as.character(bed_type))) +
  geom_boxplot(outlier.shape = NA) +
  theme(axis.text.x = element_text(angle = 90, hjust = 1),legend.title = element_blank())+
  coord_cartesian(ylim = c(0, 3)) +
  xlab("bed_type")
```

* neighbourhood_cleansed
```{r}
ggplot(data = listings3, aes(x = as.character(neighbourhood_cleansed), y = cx_scores, color = as.character(neighbourhood_cleansed))) +
  geom_boxplot(outlier.shape = NA) +
  theme(axis.text.x = element_text(angle = 90, hjust = 1),legend.title = element_blank())+
  coord_cartesian(ylim = c(0, 4)) +
  xlab("neighbourhood_cleansed")
```

* host_response_time
```{r}
ggplot(data = listings3, aes(x = as.character(host_response_time), y = cx_scores, color = as.character(host_response_time))) +
  geom_boxplot(outlier.shape = NA) +
  theme(axis.text.x = element_text(angle = 90, hjust = 1),legend.title = element_blank())+
  coord_cartesian(ylim = c(0, 4)) +
  xlab("host_response_time")
```

Transform these character variables into numeric variables
```{r}
listings4 <- listings3 %>% mutate(val1 = 1, val2 = 1, val3 = 1, val4 = 1, val5 = 1, val6 = 1)
listings4 <- listings4 %>% 
  spread(host_response_time, val1, fill = 0) %>% 
  spread(neighbourhood_cleansed, val2, fill = 0) %>% 
  spread(property_type, val3, fill = 0) %>% 
  spread(room_type, val4, fill = 0) %>% 
  spread(bed_type, val5, fill = 0) %>% 
  mutate(host_verifications = nchar(gsub('[^,]', '', host_verifications))+1,
         amenities = nchar(gsub('[^,]', '', amenities))+1) %>% 
  spread(last_review, val6, fill = 0)
```

Keep variables with the absolute value of correlation bigger than 0.1.
```{r}
corr <- as.data.frame(lapply(listings4, function(x)cor(x, listings4$cx_scores))) %>% 
  gather(key = "var", value = "correlation") %>% 
  arrange(desc(abs(correlation))) %>% 
  filter(abs(correlation)>0.15)
```

## Regression
Summary statistics
```{r}
listings_reg <- listings4 %>% 
  select(cx_scores,`2020`, host_acceptance_rate, `no response`,host_response_rate,
         host_is_superhost, amenities, `within an hour`, `Yau Tsim Mong`, `Central & Western`,
         guests_included) %>% 
  rename(Central_Western = `Central & Western`,
         within_an_hour = `within an hour`,
         Yau_Tsim_Mong = `Yau Tsim Mong`,
         no_response = `no response`,
         last_review_2020 = `2020`)
stargazer(listings_reg,type='html',title = 'Summary Statistics', out = 'summary_statistics.html')
```

Normalization
```{r}
listings_reg$amenities <- normalize(listings_reg$amenities)
listings_reg$guests_included <- normalize(listings_reg$guests_included)
listings_reg$cx_scores <- normalize(listings_reg$cx_scores, method = "center")
```

Regression Model
```{r}
listings_model <- lm(cx_scores~., listings_reg)
stargazer(listings_model,type='html',title = 'Listings Regression Model', out = 'regression_model.html')
```

RMSE
```{r}
sqrt(mean(listings_model$residuals^2))
```