---
title: "Airbnb Review Scores Rating Exploration and Prediction: Empirical Evidence from Hong Kong"
date: "15/12/2020"
authour: Minhui Ma
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, warning = FALSE)
```

## Introduction
This empirical project aims to analyze the determinants of Airbnb review scores rating and do review scores rating prediction.

This project is available on Github [`minhui-ma/Airbnb-Empirical-Projrect`](https://github.com/minhui-ma/Airbnb-Empirical-Projrect).

```{r}
# import packages
library(tidyverse)
# library(geojsonio)
library(ggplot2)
library(plotly)
library(BBmisc)
library(corrplot)
library(e1071)
# library(skimr)
library(stargazer)
library(tm)
library(tidytext)
library(DescTools)
# library(ISLR)
library(glmnet)
# library(factoextra)
library(randomForest)
library(MASS)
# set seed
set.seed(123987)
```

## Import data
```{r}
# import data
listings <- read.csv("listings.csv", header = TRUE, sep = ",")
# reviews <- read.csv("reviews.csv", header = TRUE, sep = ",")
# calendar <- read.csv("calendar.csv", header = TRUE, sep = ",")
# neighbourhoods <- read.csv("neighbourhoods.csv", header = TRUE, sep = ",")

# import map
# spdf <- geojson_read("neighbourhoods.geojson", what = "sp")
```

## Data cleaning
* Replace all empty values with NA 
* Filter rows with ```review_scores_rating``` in NA
* Drop all empty columns
* Drop columns with same value
* For missing review scores of the 6 dimensions, let them equal to ```review_scores_rating```
* Convert currency values to numeric values
* Replace date value with its year
* Convert percentage values to numeric values, and replace missing values with 0
```{r}
listings[listings==''] <- NA
listings[listings=='N/A'] <- NA

listings2 <- listings %>% filter(review_scores_rating != '')

listings2 <- listings2[!sapply(listings,function(x)all(is.na(x)))]

listings2 <- listings2 %>% dplyr::select(where(~length(unique(.)) > 1))

review_scores <- c('review_scores_accuracy','review_scores_checkin','review_scores_communication',
                   'review_scores_cleanliness','review_scores_value','review_scores_location')
for (i in review_scores){
  text <- paste("listings2$",i," <- ifelse(is.na(listings2$",i,"),listings2$review_scores_rating*0.1,listings2$",i,")",sep='')
  eval(parse(text= text))
}

listings2$price <- as.numeric(gsub('[$,]', '', listings2$price))
listings2$weekly_price <- as.numeric(gsub('[$,]', '', listings2$weekly_price))
listings2$monthly_price <- as.numeric(gsub('[$,]', '', listings2$monthly_price))
listings2$security_deposit <- as.numeric(gsub('[$,]', '', listings2$security_deposit))
listings2$cleaning_fee <- as.numeric(gsub('[$,]', '', listings2$cleaning_fee))
listings2$extra_people <- as.numeric(gsub('[$,]', '', listings2$extra_people))

var_date <- c('host_since','first_review','last_review')
for (i in var_date){
  text <- paste("listings2$",i," <- floor(as.integer(format(as.Date(listings2$",i,"),'%Y')))",sep='')
  eval(parse(text= text))
}

listings2$host_response_rate <- as.numeric(sub("%","",listings2$host_response_rate))/100
listings2$host_response_rate[is.na(listings2$host_response_rate)] <- 0
listings2$host_acceptance_rate <- as.numeric(sub("%","",listings2$host_acceptance_rate))/100
listings2$host_acceptance_rate[is.na(listings2$host_acceptance_rate)] <- 0
```

* Drop variables
- ```listing_url```, ```picture_url```, ```host_url```, ```host_thumbnail_url```, ```host_picture_url```
- ```host_name```, ```name```
- ```market```, ```state```, ```smart_location```, ```country_code```, ```country```
- ```host_listings_count```, ```host_total_listings_count```
- ```host_location```, ```host_neighbourhood```, ```street```, ```city```
- ```neighbouthood```
- ```zipcode```, ```square_feet```
- ```availability_30```, ```availability_60```, ```availability_90```, ```availability_365```
- ```last_scraped```, ```calendar_last_scraped```
- ```host_id```
- ```longitude```,```latitude```
```{r}
listings2 <- listings2 %>% 
  dplyr::select(-listing_url, -picture_url, -host_url, -host_thumbnail_url, -host_picture_url,
         -host_name, -name,
         -market, -state, -smart_location, -country_code, -country,
         -host_location, -host_neighbourhood, -street, -city,
         -host_listings_count, -host_total_listings_count, 
         -neighbourhood, 
         -zipcode, -square_feet,
         -availability_30, -availability_60, -availability_90, -availability_365,
         -last_scraped, -calendar_last_scraped,
         -host_id,
         -longitude, -latitude)
```

* Replace t with 1 and f with 0: ```host_has_profile_pic```, ```host_identity_verified```, ```host_is_superhost```, ```is_location_exact```, ```instant_bookable```, ```require_guest_profile_picture```, ```require_guest_phone_verification```
```{r}
listings2 <- listings2 %>% 
  mutate(host_has_profile_pic = ifelse(host_has_profile_pic == "t", 1, 0),
         host_identity_verified = ifelse(host_identity_verified == "t", 1, 0),
         host_is_superhost = ifelse(host_is_superhost == "t", 1, 0),
         is_location_exact = ifelse(is_location_exact == "t", 1, 0),
         instant_bookable = ifelse(instant_bookable == "t", 1, 0),
         require_guest_profile_picture = ifelse(require_guest_profile_picture == "t", 1, 0),
         require_guest_phone_verification = ifelse(require_guest_phone_verification == "t", 1, 0),)
var <- c('host_has_profile_pic','host_identity_verified','host_is_superhost','is_location_exact',
         'instant_bookable','require_guest_profile_picture','require_guest_phone_verification')
for (i in var){
  text <- paste(" listings2$",i,"[is.na(listings2$",i,")] <- 0",sep='')
  eval(parse(text= text))
}
```

* Drop variables: ```summary```,  ```space```, ```description```, ```neighborhood_overview```, ```notes```, ```transit```, ```access```, ```interaction```, ```house_rules```, ```license```, ```host_about```, ```cancellation_policy```, ```host_about```, ```cancellation_policy```
* Drop variable ```is_location_exact```: unimportant as it could be inacurate up to 150 meters http://insideairbnb.com/about.html#disclaimers
* Drop variable ```calendar_updated```: we are not interested in future data that is a subject to daily updates
```{r}
listings2 <- listings2 %>% 
  dplyr::select(-summary, -space, -description, -neighborhood_overview, -notes, -transit, -access, -interaction, -house_rules, -license, -host_about, -cancellation_policy, -is_location_exact, -calendar_updated)
```

* Replace missing values with 0: ```bathrooms```,  ```beds``` 
* Replace missing values with mean values: ```host_since```, ```security_deposit```, ```cleaning_fee```
* Replace missing values with other values: ```monthly_price```, ```weekly_price```, ```host_response_time```
```{r}
var0 <- c('bathrooms','beds','bedrooms')
for (i in var0){
  text <- paste("listings2$",i,"[is.na(listings2$",i,")] <- 0",sep='')
  eval(parse(text= text))
}

listings2$host_since[is.na(listings2$host_since)] <- floor(mean(listings2$host_since[!is.na(listings2$host_since)]))
listings2$security_deposit[is.na(listings2$security_deposit)] <- floor(mean(listings2$security_deposit[!is.na(listings2$security_deposit)]))
listings2$cleaning_fee[is.na(listings2$cleaning_fee)] <- floor(mean(listings2$cleaning_fee[!is.na(listings2$cleaning_fee)]))

listings2$weekly_price[is.na(listings2$weekly_price)] <- 7*listings2$price[is.na(listings2$weekly_price)]
listings2$monthly_price[is.na(listings2$monthly_price)] <- 30*listings2$price[is.na(listings2$monthly_price)]

listings2$host_response_time[is.na(listings2$host_response_time)] <- 'no response'
```

Remove observations with 0 review
```{r}
listings2 <- listings2 %>% filter(number_of_reviews>0)
```

* Remove outliers
```{r}
#find absolute value of z-score for each value in each column
df <- listings2 %>% dplyr::select(where(is.numeric)) %>% dplyr::select(-id, -host_since, -last_review, -first_review)
z_scores <- as.data.frame(sapply(df, function(df)(abs(df-mean(df))/sd(df))))

#only keep rows in dataframe with all z-scores less than absolute value of 3 
listings2 <- listings2[!rowSums(z_scores>3),]

#remove columns with same values
listings2 <- listings2 %>% dplyr::select(where(~length(unique(.)) > 1))
```

## Exploratory Data Analysis
### Scores correlation matrix
```{r}
listings_scores <- listings2 %>% 
  dplyr::select(review_scores_rating, 
         review_scores_accuracy, 
         review_scores_checkin, 
         review_scores_cleanliness, 
         review_scores_communication,
         review_scores_location, 
         review_scores_value) %>% 
  rename(scores = review_scores_rating, 
         accuracy = review_scores_accuracy, 
         checkin = review_scores_checkin, 
         cleanliness = review_scores_cleanliness, 
         communication = review_scores_communication,
         location = review_scores_location, 
         value = review_scores_value)
corrplot(cor(listings_scores), type = "lower", method = "number")
```

### CX scores
```review_scores_rating``` is an overall score on the AirBnb listing from 0–100. ```reviews_per_month``` is the number of reviews received by a listing per month.
```{r}
ggplot(listings2, aes(x = review_scores_rating)) + 
  geom_histogram(fill="black", colour="black", alpha = 0.25, binwidth=1)
```
skewness
```{r}
skewness(listings2$review_scores_rating)
```
kurtosis
```{r}
kurtosis(listings2$review_scores_rating)
```

```{r}
ggplot(listings2, aes(x = reviews_per_month)) + 
  geom_histogram(fill="black", colour="black", alpha = 0.25, binwidth=0.1)
```

skewness
```{r}
skewness(listings2$reviews_per_month)
```
kurtosis
```{r}
kurtosis(listings2$reviews_per_month)
```

Replace ```review_scores_rating``` with ```cx_scores``` and drop ```review_scores_rating```, ```review_scores_accuracy```, ```review_scores_checkin```, ```review_scores_cleanliness```, ```review_scores_communication```,```review_scores_location```, ```review_scores_value```, ```reviews_per_month```, ```number_of_reviews```, ```number_of_reviews_ltmh```, 
```{r}
listings3 <- listings2 %>% 
  mutate(cx_scores = normalize(review_scores_rating, method  = "range", range = c(0,1))*reviews_per_month) %>% 
  dplyr::select(-review_scores_rating, 
         -review_scores_accuracy, 
         -review_scores_checkin, 
         -review_scores_cleanliness, 
         -review_scores_communication,
         -review_scores_location, 
         -review_scores_value,
         -reviews_per_month,
         -number_of_reviews,
         -number_of_reviews_ltm)
```
```{r}
ggplot(listings3, aes(x = cx_scores)) + 
  geom_histogram(fill="black", colour="black", alpha = 0.25, binwidth=0.1)
```

### Character variables
* property_type
```{r}
ggplot(data = listings3, aes(x = as.character(property_type), y = cx_scores, color = as.character(property_type))) +
  geom_boxplot(outlier.shape = NA) +
  theme(axis.text.x = element_text(angle = 90, hjust = 1),legend.position = "none")+
  xlab("property_type")
```

* room_type
```{r}
ggplot(data = listings3, aes(x = as.character(room_type), y = cx_scores, color = as.character(room_type))) +
  geom_boxplot(outlier.shape = NA) +
  theme(axis.text.x = element_text(angle = 90, hjust = 1),legend.title = element_blank())+
  coord_cartesian(ylim = c(0, 3)) +
  xlab("room_type")
```

* bed_type
```{r}
ggplot(data = listings3, aes(x = as.character(bed_type), y = cx_scores, color = as.character(bed_type))) +
  geom_boxplot(outlier.shape = NA) +
  theme(axis.text.x = element_text(angle = 90, hjust = 1),legend.title = element_blank())+
  coord_cartesian(ylim = c(0, 2)) +
  xlab("bed_type")
```

* neighbourhood_cleansed
```{r}
ggplot(data = listings3, aes(x = as.character(neighbourhood_cleansed), y = cx_scores, color = as.character(neighbourhood_cleansed))) +
  geom_boxplot(outlier.shape = NA) +
  theme(axis.text.x = element_text(angle = 90, hjust = 1),legend.title = element_blank())+
  coord_cartesian(ylim = c(0, 3)) +
  xlab("neighbourhood_cleansed")
```

* host_response_time
```{r}
ggplot(data = listings3, aes(x = as.character(host_response_time), y = cx_scores, color = as.character(host_response_time))) +
  geom_boxplot(outlier.shape = NA) +
  theme(axis.text.x = element_text(angle = 90, hjust = 1),legend.title = element_blank())+
  coord_cartesian(ylim = c(0, 3)) +
  xlab("host_response_time")
```
### Numeric Variables
Transform these character variables into numeric variables
```{r}
listings4 <- listings3 %>% mutate(val1 = 1, val2 = 1, val3 = 1, val4 = 1, val5 = 1)
listings4 <- listings4 %>% 
  spread(host_response_time, val1, fill = 0) %>% 
  spread(neighbourhood_cleansed, val2, fill = 0) %>% 
  spread(property_type, val3, fill = 0) %>% 
  spread(room_type, val4, fill = 0) %>% 
  spread(bed_type, val5, fill = 0)
```

List out year variables
```{r}
listings4$host_since <- paste0('host_since_',listings4$host_since,sep='')
listings4$first_review <- paste0('first_review_',listings4$first_review,sep='')
listings4$last_review <- paste0('last_review_',listings4$last_review,sep='')

listings4 <- listings4 %>% mutate(val1 = 1, val2 = 1, val3 = 1)
listings4 <- listings4 %>% 
  spread(host_since, val1, fill = 0) %>% 
  spread(first_review, val2, fill = 0) %>% 
  spread(last_review, val3, fill = 0)
```

```{r}
ggplot(listings4, aes(x = host_response_rate)) + 
  geom_histogram(fill="black", colour="black", alpha = 0.25, binwidth=0.1)
```
```{r}
ggplot(listings4, aes(x = host_acceptance_rate)) + 
  geom_histogram(fill="black", colour="black", alpha = 0.25, binwidth=0.1)
```
```{r}
ggplot(listings4, aes(x = accommodates)) + 
  geom_histogram(fill="black", colour="black", alpha = 0.25, binwidth=1)
```
```{r}
ggplot(listings4, aes(x = bathrooms)) + 
  geom_histogram(fill="black", colour="black", alpha = 0.25, binwidth=1)
```
```{r}
ggplot(listings4, aes(x = bedrooms)) + 
  geom_histogram(fill="black", colour="black", alpha = 0.25, binwidth=1)
```
```{r}
ggplot(listings4, aes(x = beds)) + 
  geom_histogram(fill="black", colour="black", alpha = 0.25, binwidth=1)
```
```{r}
ggplot(listings4, aes(x = price)) + 
  geom_histogram(fill="black", colour="black", alpha = 0.25, binwidth=100)
```
```{r}
ggplot(listings4, aes(x = weekly_price)) + 
  geom_histogram(fill="black", colour="black", alpha = 0.25, binwidth=1000)
```
```{r}
ggplot(listings4, aes(x = monthly_price)) + 
  geom_histogram(fill="black", colour="black", alpha = 0.25, binwidth=5000)
```
```{r}
ggplot(listings4, aes(x = calculated_host_listings_count)) + 
  geom_histogram(fill="black", colour="black", alpha = 0.25, binwidth=10)
```
```{r}
ggplot(listings4, aes(x = calculated_host_listings_count_entire_homes)) + 
  geom_histogram(fill="black", colour="black", alpha = 0.25, binwidth=5)
```
```{r}
ggplot(listings4, aes(x = calculated_host_listings_count_private_rooms)) + 
  geom_histogram(fill="black", colour="black", alpha = 0.25, binwidth=10)
```
```{r}
ggplot(listings4, aes(x = calculated_host_listings_count_shared_rooms)) + 
  geom_histogram(fill="black", colour="black", alpha = 0.25, binwidth=1)
```

### Amenities & Host_verifications
#### nchar
```{r}
listings_nchar <- listings4 %>% 
  mutate(host_verifications = nchar(gsub('[^,]', '', host_verifications))+1,
         amenities = nchar(gsub('[^,]', '', amenities))+1)
```

```{r}
ggplot(listings_nchar, aes(x = host_verifications)) + 
  geom_histogram(fill="black", colour="black", alpha = 0.25, binwidth=1)
```

```{r}
ggplot(listings_nchar, aes(x = amenities)) + 
  geom_histogram(fill="black", colour="black", alpha = 0.25, binwidth=1)
```

```{r}
ggplot(data = listings_nchar, aes(x = host_verifications, y = cx_scores)) +
  geom_point() +
  geom_smooth(method = lm)
```

```{r}
ggplot(data = listings_nchar, aes(x = amenities, y = cx_scores)) +
  geom_point() +
  geom_smooth(method = lm)
```

Keep variables with the absolute value of correlation bigger than 0.15
```{r}
corr_nchar <- as.data.frame(lapply(listings_nchar, function(x)cor(x, listings_nchar$cx_scores))) %>% 
  gather(key = "var", value = "correlation") %>% 
  arrange(desc(abs(correlation))) %>% 
  filter(abs(correlation)>0.15)
corr_nchar
```

#### NLP
Amenities
```{r}
amenities <- listings4 %>% unnest_tokens(word, amenities, token = "regex", pattern = "\\,|\\{|\\}")
frequency_amenities <-  amenities %>% count(word) %>% arrange(desc(n))
head(frequency_amenities,20)
```
Host_verifications
```{r}
host_verifications <- listings4 %>% unnest_tokens(word, host_verifications, token = "regex", pattern = "\\,|\\[|\\]|\\'|\\s")
frequency_host_verifications <-  host_verifications %>% count(word) %>% arrange(desc(n))
head(frequency_host_verifications,10)
```

```{r}
listings_nlp <- listings4 %>% 
  mutate(air_conditioning = case_when(tolower(amenities) %like% '%air conditioning%' ~ 1, TRUE ~ 0),
         wifi = case_when(tolower(amenities) %like% '%wifi%' ~ 1, TRUE ~ 0),
         essentials = case_when(tolower(amenities) %like% '%essentials%' ~ 1, TRUE ~ 0),
         shampoo = case_when(tolower(amenities) %like% '%shampoo%' ~ 1, TRUE ~ 0),
         tv = case_when(tolower(amenities) %like% "%tv,%" ~ 1, TRUE ~ 0),
         hangers = case_when(tolower(amenities) %like% "%hangers%" ~ 1, TRUE ~ 0),
         hair_dryer = case_when(tolower(amenities) %like% "%hair dryer%" ~ 1, TRUE ~ 0),
         elevator = case_when(tolower(amenities) %like% "%elevator%" ~ 1, TRUE ~ 0),
         kitchen = case_when(tolower(amenities) %like% "%kitchen%" ~ 1, TRUE ~ 0),
         hot_water = case_when(tolower(amenities) %like% "%hot water%" ~ 1, TRUE ~ 0),
         washer = case_when(tolower(amenities) %like% '%washer%' ~ 1, TRUE ~ 0),
         laptop_friendly_workspace = case_when(tolower(amenities) %like% '%laptop-friendly workspace%' ~ 1, TRUE ~ 0),
         family_kid_friendly = case_when(tolower(amenities) %like% '%family/kid friendly%' ~ 1, TRUE ~ 0),
         iron = case_when(tolower(amenities) %like% '%iron%' ~ 1, TRUE ~ 0),
         lock_on_bedroom_door = case_when(tolower(amenities) %like% "%lock on bedroom door%" ~ 1, TRUE ~ 0),
         smoke_alarm = case_when(tolower(amenities) %like% "%smoke alarm%" ~ 1, TRUE ~ 0),
         fire_extinguisher = case_when(tolower(amenities) %like% "%fire extinguisher%" ~ 1, TRUE ~ 0),
         refrigerator = case_when(tolower(amenities) %like% "%refrigerator%" ~ 1, TRUE ~ 0),
         heating = case_when(tolower(amenities) %like% "%heating%" ~ 1, TRUE ~ 0),
         self_check_in = case_when(tolower(amenities) %like% "%self check-in%" ~ 1, TRUE ~ 0),
         phone = case_when(tolower(host_verifications) %like% "%'phone'%" ~ 1, TRUE ~ 0),
         email = case_when(tolower(host_verifications) %like% "%'email'%" ~ 1, TRUE ~ 0),
         reviews = case_when(tolower(host_verifications) %like% "%'reviews'%" ~ 1, TRUE ~ 0),
         government_id = case_when(tolower(host_verifications) %like% "%'government_id'%" ~ 1, TRUE ~ 0),
         jumio = case_when(tolower(host_verifications) %like% "%'jumio'%" ~ 1, TRUE ~ 0),
         offline_government_id = case_when(tolower(host_verifications) %like% "%'offline_government_id'%" ~ 1, TRUE ~ 0),
         selfie = case_when(tolower(host_verifications) %like% "%'selfie'%" ~ 1, TRUE ~ 0),
         identity_manual = case_when(tolower(host_verifications) %like% "%'identity_manual'%" ~ 1, TRUE ~ 0),
         facebook = case_when(tolower(host_verifications) %like% "%'facebook'%" ~ 1, TRUE ~ 0),
         work_email = case_when(tolower(host_verifications) %like% "%'work_email'%" ~ 1, TRUE ~ 0)) %>% 
  dplyr::select(-amenities, -host_verifications)
```

Keep variables with the absolute value of correlation bigger than 0.15.
```{r}
corr_nlp <- as.data.frame(lapply(listings_nlp, function(x)cor(x, listings_nlp$cx_scores))) %>% 
  gather(key = "var", value = "correlation") %>% 
  arrange(desc(abs(correlation))) %>% 
  filter(abs(correlation)>0.15)
corr_nlp
```

#### Summary statistics
```{r}
listings_reg_nchar <- listings_nchar %>% 
  dplyr::select(cx_scores,last_review_2020, host_acceptance_rate, host_is_superhost, host_response_rate, 
         `no response`, `within an hour`, amenities, last_review_2018, `Yau Tsim Mong`, 
         last_review_2017, `Central & Western`, guests_included) %>% 
  rename(Central_Western = `Central & Western`,
         within_an_hour = `within an hour`,
         Yau_Tsim_Mong = `Yau Tsim Mong`,
         no_response = `no response`)
stargazer(listings_reg_nchar,type='html',title = 'Summary Statistics', out = 'summary_statistics_nchar.html')
```

```{r}
corrplot(cor(listings_reg_nchar), type = "lower")
```

```{r}
listings_reg_nlp <- listings_nlp %>% 
  dplyr::select(cx_scores,last_review_2020, host_acceptance_rate, host_is_superhost, host_response_rate,
         `no response`, `within an hour`, self_check_in, hot_water, refrigerator, last_review_2018, 
         hair_dryer, shampoo, `Yau Tsim Mong`, hangers, last_review_2017, `Central & Western`, 
         guests_included) %>% 
  rename(Central_Western = `Central & Western`,
         within_an_hour = `within an hour`,
         Yau_Tsim_Mong = `Yau Tsim Mong`,
         no_response = `no response`)
stargazer(listings_reg_nlp,type='html',title = 'Summary Statistics', out = 'summary_statistics_nlp.html')
```

```{r}
corrplot(cor(listings_reg_nlp), type = "lower")
```

### Normalization
```{r}
# nchar
listings_reg_nchar$amenities <- normalize(listings_reg_nchar$amenities)
listings_reg_nchar$guests_included <- normalize(listings_reg_nchar$guests_included)
listings_reg_nchar$host_acceptance_rate <- normalize(listings_reg_nchar$host_acceptance_rate)
listings_reg_nchar$host_response_rate <- normalize(listings_reg_nchar$host_response_rate)
listings_reg_nchar$cx_scores <- normalize(listings_reg_nchar$cx_scores, method = "center")
# nlp
listings_reg_nlp$guests_included <- normalize(listings_reg_nlp$guests_included)
listings_reg_nlp$host_acceptance_rate <- normalize(listings_reg_nlp$host_acceptance_rate)
listings_reg_nlp$host_response_rate <- normalize(listings_reg_nlp$host_response_rate)
listings_reg_nlp$cx_scores <- normalize(listings_reg_nlp$cx_scores, method = "center")
```

## Regression
### Linear Regression
```{r}
# nchar
linear_model_nchar <- lm(cx_scores~., listings_reg_nchar)
stargazer(linear_model_nchar,type='html',title = 'Linear Regression Model', out = 'linear_regression_model_nchar.html')
#nlp
linear_model_nlp <- lm(cx_scores~., listings_reg_nlp)
stargazer(linear_model_nlp,type='html',title = 'Linear Regression Model', out = 'linear_regression_model_nlp.html')
```

RMSE
```{r}
sqrt(mean(linear_model_nchar$residuals^2))
sqrt(mean(linear_model_nlp$residuals^2))
```
We now split the samples into a training set and a test set in order to estimate the test error of linear regression, ridge regression, and the lasso.
```{r}
train = listings_reg_nlp %>% sample_frac(0.8)
test = listings_reg_nlp %>% setdiff(train)

x_train = model.matrix(cx_scores~., train)[,-1]
x_test = model.matrix(cx_scores~., test)[,-1]

y_train = train %>%
  dplyr::select(cx_scores) %>%
  unlist() %>%
  as.numeric()
y_test = test %>%
  dplyr::select(cx_scores) %>%
  unlist() %>%
  as.numeric()
```

RMSE
```{r}
linear_train <- lm(cx_scores~., train)
linear_pred <- predict(linear_train, newx = x_test)
sqrt(mean((linear_pred - y_test)^2))
```

### Ridge Regression
```{r}
# outcome
y <- listings_reg_nlp$cx_scores

# Predictors as matrix 
x <- listings_reg_nlp %>% dplyr::select(-cx_scores) %>% data.matrix()

# Set up the hyperparameter, lambda - this is the strength of the penalty for each residual 
lambdas <- 10^seq(3, -2, by = -.1)

# Find optimal lambda using cross-validation - running the model many times for different values of lambda
cv_ridge_model <- cv.glmnet(x, y, alpha = 0, lambda = lambdas)
plot(cv_ridge_model)
```

So we now have the optimal lambda for our value. We can extract this value to work with it:
```{r}
opt_lambda <- cv_ridge_model$lambda.min
opt_lambda
```

Now we have our trained models as below:
```{r}
ridge_model <- cv_ridge_model$glmnet.fit
summary(ridge_model)
```

We can also visualize the coefficients as below, where each curve is a variable
```{r}
plot(ridge_model, label = TRUE)
```

And we can see how good the training model is: 
```{r}
ridge_y_pred <- predict(ridge_model, s = opt_lambda, newx = x)

# Sum of Squares Total and Error
sst <- sum((y - mean(y))^2)
sse <- sum((ridge_y_pred - y)^2)

# R squared
rsq <- 1 - sse / sst
rsq
```

RMSE
```{r}
ridge_train <- glmnet(x_train, y_train, alpha=0, lambda = lambdas)
ridge_pred <- predict(ridge_train, s = opt_lambda, newx = x_test)
sqrt(mean((ridge_pred - y_test)^2))
```

## Lasso Regression
```{r}
lasso_model <- glmnet(x, y, alpha = 1, lambda = lambdas)
plot(lasso_model, label = TRUE)    # Draw plot of coefficients
```

Notice that in the coefficient plot that depending on the choice of tuning parameter, some of the coefficients are exactly equal to zero. We now perform cross-validation and compute the associated test error:
```{r}
cv_lasso_model <- cv.glmnet(x, y, alpha = 1) # Fit lasso model on training data
plot(cv_lasso_model) # Draw plot of training MSE as a function of lambda
```

And we can see how good the training model is: 
```{r}
opt_lambda <- cv_lasso_model$lambda.min
lasso_y_pred <- predict(lasso_model, s = opt_lambda, newx = x)

# Sum of Squares Total and Error
sst <- sum((y - mean(y))^2)
sse <- sum((lasso_y_pred - y)^2)

# R squared
rsq <- 1 - sse / sst
rsq
```

RMSE
```{r}
lasso_train <- glmnet(x_train, y_train, alpha=1, lambda = lambdas)
lasso_pred <- predict(lasso_model, s = opt_lambda, newx = x_test) # Use best lambda to predict test data
sqrt(mean((lasso_pred - y_test)^2))
```

### Random Forest
```{r}
oob.err=double(13)
test.err=double(13)
#mtry is the number of variables randomly chosen at each split
for(mtry in 1:13) 
{
  rf=randomForest(cx_scores ~ . , data = train,mtry=mtry,ntree=400) 
  oob.err[mtry] = rf$mse[400] #Error of all Trees fitted
  
  pred<-predict(rf,test) #Predictions on Test Set for each Tree
  test.err[mtry]= with(test, mean((cx_scores - pred)^2)) #Mean Squared Test Error
  
  cat(mtry," ") #printing the output to the console
}
```
```{r}
matplot(1:mtry, cbind(oob.err,test.err), pch=19, col=c("red","blue"), type="b", ylab="Mean Squared Error", xlab="Number of Predictors Considered at each Split")
legend("topright", legend=c("Out of Bag Error","Test Error"), pch=19, col=c("red","blue"))
```

```{r}
rf_model <- randomForest(cx_scores ~ . , data = train, mtry = 5, ntree=400)
rf_model
```
```{r}
plot(rf_model)
```

RMSE
```{r}
rf_pred <- predict(rf_model,test)
sqrt(mean((rf_pred - y_test)^2))
```
